---
title: "Homework 5"
author: "Cong Zhang"
date: 2021-04-28
output: html_document
---

This is my solution to Homework 5. 

```{r include = FALSE, message = FALSE}
library(tidyverse)
library(caret)
library(e1071)
library(mlbench)
library(ISLR)
library(kernlab)

knitr::opts_chunk$set(
	fig.width = 6, 
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

set.seed(1)
```

### Create a training set containing a random sample of 800 observations, and a test set containing the remaining observations.

Import data.
```{r message = FALSE}
data(OJ)
oj_df = OJ %>% 
  janitor::clean_names()

set.seed(1)
row_train <- createDataPartition(y = oj_df$purchase, p = 799/1070, list = FALSE)

# training data
x_train <- model.matrix(purchase ~ ., oj_df)[row_train,-1]
y_train <- oj_df$purchase[row_train]
data_train <- subset(oj_df[row_train,])

# test data
x_test <- model.matrix(purchase ~ ., oj_df)[-row_train,-1]
y_test <- oj_df$purchase[-row_train]
data_test <- subset(oj_df[-row_train,])
```


### (a) Fit a support vector classifier (linear kernel) to the training data with Purchase as the response and the other variables as predictors. What are the training and test error rates?

Fit a support vector classifier (linear kernel).
```{r message = FALSE}
ctrl = trainControl(method = "cv")

set.seed(1)
svml_fit = train(purchase ~ .,
                 data = data_train,
                 method = "svmLinear",
                 preProcess = c("center", "scale"),
                 tuneGrid = data.frame(C = exp(seq(-5, 2, len = 100))),
                 trControl = ctrl)

ggplot(svml_fit, highlight = TRUE, xTrans = log)

svml_fit$bestTune

svml_fit$finalModel
```


Calculate the training and test error rates.
```{r}
pred_svml_train = predict(svml_fit)

mean(data_train$purchase != pred_svml_train)

pred_svml_test = predict(svml_fit, newdata = data_test, type = "raw")

confusionMatrix(data = pred_svml_test,
                reference = data_test$purchase)

mean(data_test$purchase != pred_svml_test)
```

From the result, we could see the training error rate is `r mean(data_train$purchase != pred_svml_train)*100`%, and the test error rate is `r mean(data_test$purchase != pred_svml_test)*100`%.


### (b) Fit a support vector machine with a radial kernel to the training data. What are the training and test error rates?

Fit a support vector machine with a radial kernel.
```{r message = FALSE}
svmr_grid = expand.grid(C = exp(seq(-5, 2, len = 30)),
                        sigma = exp(seq(-6, 0, len = 15)))

set.seed(1)
svmr_fit = train(purchase ~ .,
                 data = data_train,
                 method = "svmRadial",
                 preProcess = c("center", "scale"),
                 tuneGrid = svmr_grid,
                 trControl = ctrl)

ggplot(svmr_fit, highlight = TRUE, xTrans = log)

svmr_fit$bestTune

svmr_fit$finalModel
```


Calculate the training and test error rates.
```{r}
pred_svmr_train = predict(svmr_fit)

mean(data_train$purchase != pred_svmr_train)

pred_svmr_test = predict(svmr_fit, newdata = data_test, type = "raw")

confusionMatrix(data = pred_svmr_test,
                reference = data_test$purchase)

mean(data_test$purchase != pred_svmr_test)
```

From the result, we could see the training error rate is `r mean(data_train$purchase != pred_svmr_train)*100`%, and the test error rate is `r mean(data_test$purchase != pred_svmr_test)*100`%.


Compare the two models.
```{r message = FALSE}
resamp = resamples(list(svml = svml_fit,
                        svmr = svmr_fit))
summary(resamp)
bwplot(resamp)
```

